Twists of supersymmetric gauge theories

### 2020-01-13 paper.tex
caption for figure

\end{tikzpicture}
\caption{Orbits of square-zero supercharges.}
\label{fig:superchargeorbits}
\end{figure}

>>>>

\end{tikzpicture}
\caption{This figure shows the orbits of square-zero supercharges in each dimension.  The labels indicate each orbit: the number refers to the rank, and the subscript indicates the situations where the supercharges of a given rank split into multiplet orbits.  Each column is labelled by a dimension, and each row by the number of invariant directions of the supercharge.  Colours indicate the maximal supersymmetry algebra where the given supercharges live, so red indicates supercharges defined in algebras with 16 supercharges, orange those with 8 supercharges, and yellow those with 4 supercharges.}
\label{fig:superchargeorbits}
\end{figure}
